RadLib: a radiative property model library for CFD

### 2021-09-28 manuscript/manuscript.tex
fixing whitespace issues to allow comparison with previous revision

    The direct solution of the spectral RTE using so-called line-by-line calculations, in which the RTE is solved for
    each
    individual spectral line, is computationally prohibitive for most practical configurations and is used primarily
    for model
    validation. Some band models rely on estimated or averaged "line-of-sight" property values that cannot be directly
    incorporated into the RTE. Modern band models require high-resolution databases and reorder emission levels rather than averaging across sequential
    absorption bands, but these can lose accuracy when applied to nonhomogeneous media and may still require large numbers of
    RTE evaluations \citep{Modest_2016}.

@@

    The particular version of the model implemented is from the Turbulent Nonpremixed Flames (TNF) workshop \cite{TNF}. This is a long-running collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}. The workshop includes a number of laboratory jet flames that have been extensively researched for flame temperature, velocity, and composition profiles, and these serve as target flames for computational scientists to validate simulations and models. The PM model implemented here is the one advocated (and hence widely used) by the TNF workshop.

    For each species, the PM model provides the absorption coefficient as a fourth or fifth order polynomial fit in one
    of two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
    Ultimately, the model accommodates temperatures between 300 K and 2500 K. See
    \cite{TNF} for details and references. The PM model here considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
    The last two species have lower absorption than the first two, but are included because \ce{CH4} and syngas
    (consisting of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in the TNF flames
    in high concentrations in the fuel stream. (\ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.)

@@

    RadLib installation is automated with CMake. Inside the downloaded \texttt{radlib} folder, the user must create a
    \texttt{build} directory and navigate into it. From there, the user executes the following commands in order:
    \begin{enumerate}
        \item \texttt{cmake ..}
        \item \texttt{make}
        \item \texttt{make install}
    \end{enumerate}
    Project options can specified by editing the top-level
    \texttt{CMakeLists.txt} file where the options are clearly marked. These can also be specified at the command
    line. Options include specifying the system installation location, which defaults to \texttt{radlib/installed};
    options to build the Python and Fortran interfaces; options to build examples for C++, Python, and Fortran; and
    an option to build the documentation. Refer to the included \texttt{README} files for additional information.

>>>>

The direct solution of the spectral RTE using so-called line-by-line calculations, in which the RTE is solved for each individual spectral line, is computationally prohibitive for most practical configurations and is used primarily for model validation. Some band models rely on estimated or averaged "line-of-sight" property values that cannot be directly incorporated into the RTE. 
%dol
Modern band models require high-resolution databases and reorder emission levels rather than averaging across sequential absorption bands, but these can lose accuracy when applied to nonhomogeneous media and may still require large numbers of RTE evaluations \citep{Modest_2016}.

@@

The particular version of the model implemented is from the Turbulent Nonpremixed Flames (TNF) workshop \cite{TNF}. This is a long-running collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}. The workshop includes a number of laboratory jet flames that have been extensively researched for flame temperature, velocity, and composition profiles, and these serve as target flames for computational scientists to validate simulations and models. The PM model implemented here is the one advocated (and hence widely used) by the TNF workshop. For each species, the PM model provides the absorption coefficient as a fourth or fifth order polynomial fit in one of two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.  Ultimately, the model accommodates temperatures between 300 K and 2500 K. See \cite{TNF} for details and references. The PM model here considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.  The last two species have lower absorption than the first two, but are included because \ce{CH4} and syngas (consisting of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in the TNF flames in high concentrations in the fuel stream. (\ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.)

@@

RadLib installation is automated with CMake. Inside the downloaded \texttt{radlib} folder, the user must create a \texttt{build} directory and navigate into it. From there, the user executes the following commands in order: 
%
\begin{enumerate}
    \item \texttt{cmake ..}
    \item \texttt{make}
    \item \texttt{make install}
\end{enumerate}
%
Project options can specified by editing the top-level \texttt{CMakeLists.txt} file where the options are clearly marked. These can also be specified at the command line. Options include specifying the system installation location, which defaults to \texttt{radlib/installed}; options to build the Python and Fortran interfaces; options to build examples for C++, Python, and Fortran; and an option to build the documentation. Refer to the included \texttt{README} files for additional information.
